---
title: "json_to_txt"
author: "Matthew Malcher"
date: "21 June 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(jsonlite)
```

# Introduction

NHSD have published a [guide](https://digital.nhs.uk/binaries/content/assets/website-assets/services/data-access-environment-dae/accessing-hes-with-dae.pdf) on how to access HES using DAE. This goes through
the process of how to export a query, which notes that the query is output in
JSON format, but does not tell you how to extract the plaintext of the query
you ran.
 
This document shows how to take a query JSON downloaded from DAE and extract
the plaintext query.

# Demo

Define the name of the JSON file downloaded by HUE
```{r}
query_name <- 'los_interface_xcheck.json'
```

Read a function written to extract queries from HUE JSON files.
```{r}
source('get_query.R')
```

Apply this function to get the SQL code
```{r}
sql_code <-
  get_query_from_json(
    json_file = file.path('queries', 
                          query_name)
  )
```

Write the query out to a new file, named using the JSON file name
```{r}
fileConn <- 
  file(file.path('output', sub('.json','.txt', query_name)))

writeLines(sql_code, fileConn)

close(fileConn)
```

